The Place of the Local Group in the Cosmic Web

### 2014-08-02 paper/main.tex

\title{The Place of the Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^2$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrofísica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
}
\email{je.forero@uniandes.edu.co}

\begin{abstract}
In this Letter we explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$ CDM cosmology.
We use a description for the cosmic web that uses the Hessian of the
gravitational potential to classify a nieghborhodd in the simulation
as either peak, sheet, filament or voids. We find that the LG pairs
are preferentially located in filaments and sheets. Locally their
locations are also located in a narrow range of overdensity
$0<\delta<4$, ellipticity $0.1<e<1.0$ and prolateness
$-0.5<p<0.5$. Furthermore we find a strong anti-alignment between the
LG angular momentum vector and the filament lines and the sheet 
planes.  
\end{abstract}

@@

All this combination of features make LG analogues very rare to
find. Using numerical simulatons \citet{lganalogues} found less than
$2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
similar environment. Furthermore, if we select pairs constrained
within $2\sigma$ error fron current observational measurements of the
velocity components and distance to M31, there are only $88$ systems
in a cube of $250$ \hmpc side.

@@

To construct a sample of the MW-M31 pairs at $z\approx 0$, we use a
series of simulation snapshots  at $z<0.1$ (i.e. in the last $\approx
1.3$ Gyr before present) spaced by $\approx 150-250$ Myr. This is done
because a particular configuration of MW and M31 is transient and
corresponds to a relatively small number of systems at one
snapshot. By using multiple snapshots we can increase the sample of
systems in such configuration during a period of time in which secular
cosmological evolution is small.

Pairs are selected allowing a wide range of masses, following an
isolation critera, constraining by orbital measurements such as
radial, tangential velocity and separation of the pair, and local
environment constrains such as local velocity dispersion and local
overdensity within a sphere of radius $5$ \mpc. A full description of
the selection criteria can be found in \citet{lganalogues,sat}.

We define two samples according to the tolerance in the selection constraints:
A sample named $2\sigma$, correspondig to LG analogues constrained by
two times the observational errors in the orbital values (radial
velocity, tangential velocity, and separation), and a more relaxed
sample named $3\sigma$ for LG analogues constrained by three times
observational errors accordingly. The number of pairs in each sample
is $46$ and $120$ respectively, notice we have less pairs than in
\citet{lganalogues} results, since we removed pairs which are too
close at $z=0$, i.e. their virial radii overlaps, also we removed a
couple pairs that merged or change their mass more than $20\%$ at
present time since they were detected at $z<0.1$.

We also have a third general sample that we use as a control for our
results. {\bf What are the criteria for this sample?}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_n_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_n_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_n_all_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the normal vector
$\hat{n}$, and the eigenvectors defining the cosmic web.
    \label{fig:alignment}}  
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_r_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_r_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_r_all_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the unit
  vector linking the two halos, $\hat{r}$, and the eigenvectors
  defining the cosmic web.
    \label{fig:alignment_r}}  
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{median_mass_fraction.pdf} 
\caption{Mass dependency of the fraction of pairs in the different
  environemnts.
\label{fig:median_fraction}}
\end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{scheme.pdf} 
    \caption{Schematic picture of the strongest alignment tendencies in
      the the General and $2\sigma$-$3\sigma$ samples. The alignment
      between the peculiar velocities and the $\hat{e}_3$ eigenvector was
      reported in \citet{ForeroRomero2014} for all halos regardles of its
      mass. 
      \ref{fig:alignment}. 
      \label{fig:scheme}}
  \end{center}
\end{figure}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.49\textwidth]{alignments_jj_all_environments.pdf}
\end{center}
\caption{Alignment between the two angular momentum vectors of the two
  halos in the pair.
    \label{fig:jj_alignment}}  
\end{figure*}

@@

\begin{table*}
\begin{center}
\begin{tabular}{ccccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 4 (8.7) & 24 (52.2) &  17 (36.7) & 1 (2.2)\\
3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
General ($12.1<\log_{10} M_{\rm h}/\Msun<12.3$)& 8 (1.4) & 334 (55.5) & 259
(43.0) & 1 (0.1)\\\hline\hline  
\end{tabular}
\caption{
Number of pairs in the four different kinds of environments. In
parethesis the same number as a percentage of the
total population. 
\label{table:web_type}}
\end{center}
\end{table*}

@@

We now explore the alignment of the pairs with respect to the cosmic
web. First we define the unit vector $\hat{r}$ that links the two
halos. Then, we compute the dot product of $\hat{r}$ and each one of
the three eigenvectors for pair in the three samples. In Figure
\ref{fig:alignment} we show the main result of that study, it
presents the cumulative distribution of
$\mu\equiv\hat{e}_3\cdot\hat{r}$ for pairs located in filaments and
sheets. The straight line corresponds to the expected result for a
random vector distribution.

From this Figure we first see that there is a clear distinct behavior
between the general samples and the 3$\sigma$-2$\sigma$ samples. The
general sample tenst to be aligned along the $\hat{e}_3$ vector, the
3$\sigma$ sample does not show any strong alignment and the 2$\sigma$
pairs tend to be perpendicular to the $\hat{e}_3$ vector and slightly
parallel to $\hat{e}_1$. These trends hold in filaments and walls.

Let's focus on filaments first. That result means that in the general
sample the two halos tend to lie along the filament, while in the
2$\sigma$-3$\sigma$ samples they are located perpendicular to the
filament. If one considers that in these samples the motion is radial,
that means that the pairs are moving into the filament.

In the case of sheets, the pairs in the general sample tend to lie on
the sheet plane along the direction of the slowest collapsing
direction. In the 2$\sigma$ samples the pairs are not constrained to
the plane anymore and are perpendiculat to the $\hat{e}_3$
vector. Considering the preferential radial motion of these pairs,
that mens that the pairs are moving into the pancake all over a plane that
is itself perpendicular to the sheet.

@@

Figure \ref{fig:density} shows that the range of overdensities for the
general pair sample spans almost two orders of magnitude from
underdense regions $\delta<0$ to high density regions $\delta\sim 30$,
with a distribution peaking around $\delta \sim 0$. In contrast the
$2\sigma$ and $3\sigma$ samples are located within a narrower range of
overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1.5$. This is
consistent with the fact that these samples are mostly found in
filaments and sheets.

Figure \ref{fig:ELL_PROL} presents the cumulative distribution for
the ellipticity and prolateness. The general sample presents a wide
range in ellipticity that can range from $-30<e<30$. For the $2\sigma$
and $3\sigma$ samples most of the pairs are now located in a narrow
range for ellipticities in the range $0.1<e<1.0$. This condition on
the ellipticity together with the fact that $\delta>0$ implies that
the prolateness in these samples must be bounded by
$-1.0<p<1.0$. We actually find that they most of the pairs are bounded
to an even narrower range $0.5<p<0.5$.

Figure \ref{fig:delta_FA} shows two panels with the joint scatter plot
for the ellipticity and the prolateness as a function of the
overdensity. For clarity we only include the general and $3\sigma$
samples. In the left panel (ellipticity) we see the a simple cut in
the overdensity is not enough to explain the narrow ranges in the
ellipticity; the LG pairs in the $3\sigma$ sample are located towards
low ellipticity values. In the right panel (prolateness) we find a
similar situation; a cut in the overdensity would produced a wider
distribution in prolateness values than the one featured by the
$3\sigma$ sample.

@@

@@

\section*{Acknowledgements}

>>>>

\title{The Place of the Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^2$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
}
\email{je.forero@uniandes.edu.co}

\begin{abstract}
In this Letter we explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$CDM cosmology.
We use the Hessian of the gravitational potential to define the cosmic web, 
where regions are classified as either peak, sheet, filament or void.
%We use a description for the cosmic web that uses the Hessian of the
%gravitational potential to classify a neighborhod in the simulation
%as either peak, sheet, filament or void. 
Results indicate: 
i) The LG pairs are preferentially located in filaments and sheets,
ii) There is a strong signature that LG pairs orientation depends on the cosmic web, 
in particular for pairs in filaments/sheets the orbital angular momentum tends to be perpendicular to the filament direction or the sheet plane.
iii) They are located in in a narrow range of local overdensity $0<\delta<4$, 
ellipticity $0.1<e<1.0$ and prolateness $-0.5<p<0.5$. 
%Furthermore we find a strong anti-alignment between the
%LG angular momentum vector and the filament lines and the sheet planes.  
\end{abstract}

@@

All this combination of features make LG analogues very rare to
find. Using numerical simulatons \citet{lganalogues} found less than
$2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
similar environment. Furthermore, if we select pairs constrained
within $2\sigma$ error fron current observational measurements of the
velocity components and distance to M31, there are only $46$ systems
in a cube of $250$ \hmpc side.

@@

To construct a sample of the MW-M31 pairs at $z\approx 0$, we use a
series of simulation snapshots  at $z<0.1$ (since the last $\approx
1.3$ Gyr) spaced by $\approx 150-250$ Myr. This is done
because a particular configuration of MW and M31 is transient and
corresponds to a relatively small number of systems at one
snapshot. By using multiple snapshots we can increase the sample of
systems in such configuration during a period of time in which secular
cosmological evolution is small.

The LG analogues or General sample in this paper are pairs selected in relative isolation,
and in a wide range of masses from  $M_{200c}=5 \times 10^{10}$ \msun $ $ to $ 5 \times 10^{13}$ \msun. 
Isolation criteria includes a pair closer than $1.3$\mpc, and with no massive neighbors within $5$\mpc.
In addition we require that pairs have no Virgo-like neighbor halo with mass $M_{200c}>1.5 \times 10^{14}\ \rm M_{\odot}$ within $12$ Mpc. 
We have $5480$ pairs under these general criteria.
A full description of the selection criteria can be found in \citet{lganalogues,sat}.

We also define two subsamples more closely related to the MW-M31 
dynamics  according to the tolerance in additional constraints:
A sample named $2\sigma$, correspondig to LG analogues constrained by
two times the observational errors in the orbital values (radial
velocity, tangential velocity, and separation), and a more relaxed
sample named $3\sigma$ for LG analogues constrained by three times
observational errors accordingly. The number of pairs in each sample
is $46$ and $120$ respectively, notice we have less pairs than in
\citet{lganalogues} results, since we removed pairs which are too
close at $z=0$, i.e. their virial radii overlaps, also we removed a
couple pairs that merged or change their mass more than $20\%$ at
present time since they were detected at $z<0.1$.

%We also have a third general sample that we use as a control for our
%results.

@@

\begin{table*}
\begin{center}
\begin{tabular}{ccccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 4 (8.7) & 24 (52.2) &  17 (36.7) & 1 (2.2)\\
3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
General ($12.1<\log_{10} M_{\rm h}/\Msun<12.3$)& 8 (1.4) & 334 (55.5) & 259
(43.0) & 1 (0.1)\\
General & 1312 (23.9) & 1472 (26.9) & 1769 (32.3) & 927 (16.9)\\

\hline\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environments. In
parethesis the same number as a percentage of the
total population.
\label{table:web_type}}
\end{center}
\end{table*}

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{histogram_mass_distro.pdf}
\caption{Mass distribution of pairs in the different environments
for the General sample.
Dashed regions correspond to the mass ranges of $2\sigma$ and $3\sigma$ samples.
\label{fig:median_fraction}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_n_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_n_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_n_all_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the normal vector to the pair orbit
$\hat{n}$, and the eigenvectors defining the cosmic web.
    \label{fig:alignment}}  
\end{figure}

%\begin{figure}
%  \begin{center}
%    \includegraphics[width=0.48\textwidth]{scheme.pdf}
%    \caption{Schematic picture of the strongest alignment tendencies in
%      the the General and $2\sigma$-$3\sigma$ samples. The alignment
%      between the peculiar velocities and the $\hat{e}_3$ eigenvector was
%      reported in \citet{ForeroRomero2014} for all halos regardles of its
%      mass.
%      \label{fig:scheme}}
%  \end{center}
%\end{figure}

%\begin{figure}
%\begin{center}
%  \includegraphics[width=0.48\textwidth]{alignments_e1_r_all_environments.pdf} 
%  \includegraphics[width=0.48\textwidth]{alignments_e2_r_all_environments.pdf} 
%  \includegraphics[width=0.48\textwidth]{alignments_e3_r_all_environments.pdf} 
%\end{center}
%\caption{Cumulative distributions for the alignment between the unit
%  vector linking the two halos, $\hat{r}$, and the eigenvectors
%  defining the cosmic web.
%    \label{fig:alignment_r}}  
%\end{figure}

%\begin{figure}
%\begin{center}
%  \includegraphics[width=0.48\textwidth]{histogram_mass_distro.pdf} 
%\caption{Mass dependency of the fraction of pairs in the different
%  environemnts.
%\label{fig:median_fraction}}
%\end{center}
%\end{figure}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.49\textwidth]{alignments_jj_all_environments.pdf}
\end{center}
\caption{Alignment between the two angular momentum vectors of the two
  halos in the pair.
    \label{fig:jj_alignment}}  
\end{figure}

@@

This difference between the general and the restricted samples is mostly due 
the mass ranges covered by each sample. 
In \citet{lganalogues} the mass range covered by $2\sigma$ and $3\sigma$ 
is very narrow and it is used to constraint the LG mass, then we show 
also in table \ref{table:web_type} a subsample of the General sample
having a similar mass range to $2\sigma$ and $3\sigma$, and it reproduces 
similar environment fractions.

A more clear view of this environment dependency and pair mass is shown in
figure \ref{fig:median_fraction}, where we show the mass distribution of pairs
in the different environments, then high mass pairs tend to be located in 
peaks and filaments, and less massive ones in voids and sheets.
Dashed regions represent the $68\%$ confidence intervals of the mass 
distributions of $2\sigma$ and $3\sigma$ samples.

@@

We explore the alignment of the pairs with respect to the cosmic
web. 
We define the unit vector $\hat{n}$, normal to the pair orbital plane 
computed from the pair positions and relative velocity.
%First we define the unit vector $\hat{r}$ that links the two
%halos. 
Then, we compute the dot product of $\hat{n}$ and each one of
the three eigenvectors for the three samples.

In Figure
\ref{fig:alignment} we show the main result of that study, it
presents the cumulative distribution of
$\mu\equiv\hat{e}_i\cdot\hat{n}$ for the three eigenvectors $i=1,2,3$. 
Lines indicate the different samples.
The straight line corresponds to the expected result for a
random vector distribution.

From this Figure we can see two important features:
First, there is a strong anti-alignment signature between $\hat{n}$ 
and the third eigenvector, and this signature reverses with the first eigenvector.
However, in the case of the second eigenvector, no significant deviations are found.
Second, for $\hat{e}_3$ vector the anti-alignment become stronger for 
the samples more closely related to the LG, then for 2$\sigma$ it is 
stronger than for 3$\sigma$, and the latter is stronger than for General 
sample.

%Figure \ref{fig:scheme} depicts a scheme of the alignment tendencies
%for pairs in all samples, where the pair members positions and 
%velocities tend to align with $\hat{e}_3$ vector.
%The alignment between the peculiar velocities and the $\hat{e}_3$ 
%eigenvector was already reported in \citet{ForeroRomero2014} for all
% halos regardles of its mass.

Quantitatively, the anti-alignment feature found with the $\hat{e}_3$ 
vector means that for 2$\sigma$ sample, $\sim 50\%$ pairs have $\mu<0.2$,
and $\sim 75\%$ pairs have $\mu<0.4$.
We also test that does not change significantly on environment type, in particular 
these trends hold very well for pairs in filaments and walls.

If we consider only pairs in filaments, we have that the pair orbit tends
to be perpendicular to the filament direction, and both pair members lie 
along the filament, if we recall the 3$\sigma$-2$\sigma$ samples are 
constrained with a mostly radial velocity component, then the pairs 
are moving into the filament.
In the case of sheets, we have the pair orbital plane  tend to lie within
 the sheet plane.

These alignment features are in agreement with the scenario that pairs 
created in-situ or falling into a filament/wall align their orbits with 
the large scale structure in a relaxation process where pair members
tend to moves along the slowest collapsing directions.
However, the most intriguing feature is the dependence of this alignment
with how close we represent the LG, is still not clear.
We explore if the pair masses are responsible of this, but we found 
no dependence at all.

In Figure \ref{fig:median_alignment_n} we show the relation between the median 
of $\mu\equiv\hat{e}_i\cdot\hat{n}$ and mass for the general sample, and found 
no significant relation.
Lines in the figure show the median $\mu$-mass relation for the three 
eigenvectors in the General sample.
Dots represent the median $\mu$ for the three eigenvectors in the 
2$\sigma$-3$\sigma$ samples.
In the case of $\|\hat{e}_3\cdot\hat{n}\|$, the figure clearly shows for a fixed mass
range around $1.5-2.0 \times 10^{10}$ \msun, that the median $\mu$ decreases as we
better constraint the LG samples, being larger for General sample and smaller for 
2$\sigma$ sample accordingly.

%From this Figure we first see that there is a clear distinct behavior
%between the general samples and the 3$\sigma$-2$\sigma$ samples. The
%general sample tend to be aligned along the $\hat{e}_3$ vector, the
%3$\sigma$ sample does not show any strong alignment and the 2$\sigma$
%pairs tend to be perpendicular to the $\hat{e}_3$ vector and slightly
%parallel to $\hat{e}_1$. These trends hold in filaments and walls.

%Let's focus on filaments first. That result means that in the general
%sample the two halos tend to lie along the filament, while in the
%2$\sigma$-3$\sigma$ samples they are located perpendicular to the
%filament. If one considers that in these samples the motion is radial,
%that means that the pairs are moving into the filament.

%In the case of sheets, the pairs in the general sample tend to lie on
%the sheet plane along the direction of the slowest collapsing
%direction. In the 2$\sigma$ samples the pairs are not constrained to
%the plane anymore and are perpendiculat to the $\hat{e}_3$
%vector. Considering the preferential radial motion of these pairs,
%that mens that the pairs are moving into the pancake all over a plane that
%is itself perpendicular to the sheet.

@@

Figure \ref{fig:median_overdensity} shows dependency of overdensity,
ellipciticy, and prolateness on pair mass for the different samples.
General sample is represented by the solid lines with the associated 
errors covered by the shaded region.

Left panel shows the overdensity dependence on mass where higher mass
pairs are located in high density regions.
The $2\sigma$ and $3\sigma$ samples having a narrower mass range as 
shown in previous figure, are consequently located within a narrower 
range of overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1$. 
This is also consistent with the fact that these samples are mostly 
found in filaments and sheets. 
Average overdensity of $2\sigma$ and $3\sigma$ samples show no 
significant difference from the General sample within the same mass 
range.

%Figure \ref{fig:density} shows that the range of overdensities for the
%general pair sample spans almost two orders of magnitude from
%underdense regions $\delta<0$ to high density regions $\delta\sim 30$,
%with a distribution peaking around $\delta \sim 0$. In contrast the
%$2\sigma$ and $3\sigma$ samples are located within a narrower range of
%overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1.5$. This is
%consistent with the fact that these samples are mostly found in
%filaments and sheets.

Middle and right panels show web ellipciticy and absolute prolateness
dependence on mass. Again we noticed that within the same mass range,
the $2\sigma$ and $3\sigma$ average ellipciticy and prolateness does not
differ significantly from General sample.
For the $2\sigma$ and $3\sigma$ samples most of the pairs are located
in a narrow range for ellipticities in the range $0.1<e<1.0$, and
prolateness $0.5<p<0.5$.

%the cumulative distribution for
%the ellipticity and prolateness. The general sample presents a wide
%range in ellipticity that can range from $-30<e<30$. For the $2\sigma$
%and $3\sigma$ samples most of the pairs are now located in a narrow
%range for ellipticities in the range $0.1<e<1.0$. This condition on
%the ellipticity together with the fact that $\delta>0$ implies that
%the prolateness in these samples must be bounded by
%$-1.0<p<1.0$. We actually find that they most of the pairs are bounded
%to an even narrower range $0.5<p<0.5$.

%Figure \ref{fig:delta_FA} shows two panels with the joint scatter plot
%for the ellipticity and the prolateness as a function of the
%overdensity. For clarity we only include the general and $3\sigma$
%samples. In the left panel (ellipticity) we see the a simple cut in
%the overdensity is not enough to explain the narrow ranges in the
%ellipticity; the LG pairs in the $3\sigma$ sample are located towards
%low ellipticity values. In the right panel (prolateness) we find a
%similar situation; a cut in the overdensity would produced a wider
%distribution in prolateness values than the one featured by the
%$3\sigma$ sample.

\subsection{Spin and Orbital Angular Momentum}

In $4.2$ we defined the unit vector $\hat{n}$, normal to the pair 
orbital plane which can be asociated with the orbital angular 
momentum direction $\hat{J}$.
There, we show several alignment features of the pair orbital
momentum with the environment.
In this subsection we explore the alignement of the individual spin
angular momentum of each pair member $\hat{j_A}$ and $\hat{j_B}$ with
each other and with the orbital angular momentum.

We show in figure \ref{fig:jj_alignment} the cumulative distribution of
dot product between the spin of both members in the pair.
We found a slight alignment of spin vectors for the $2\sigma$ sample.
However, we found no significant alignment between spin and orbital angular 
momentum for any sample.

In the LG, the angle between MW and M31 spin is $\sim60^{\circ}$ and the
angles between spins and orbital angular momentum are $\sim33^{\circ}$
and $\sim76^{\circ}$ for MW and M31 respectively \citep{2012ApJ...753....9V}.
Then the LG show no particular alignement aswell.

@@

We explored the characteristics of the LG location in the cosmic web.

LG pairs are preferentially located in filaments and sheets. The mass range
of the pairs sample plays an important role in the fractions for each environment
type as shown in table $1$ and figure $1$.

There is a clear anti-alignment between the third eigenvector and the vector normal 
to the pair orbital plane. This feature is not mass dependant as can be shown in
figure $3$.
For pairs in filaments this means the pair orbit tends to be perpendicular to the 
filament direction, and both pair members lie along the filament, and in the case 
of pairs in sheets, we have the pair orbital plane lie in the sheet plane.
We also found this anti-alignment becomes stronger for the samples being more 
closely related to the LG, it means it is stronger for $2\sigma$ sample.
All these alignment features are consistent with pair orbits relaxing their 
movements towards the slowest collapsing directions at larger scales.

LG pairs are located in a narrow range of local overdensity, ellipciticy and prolateness.
And this is consistent with the narrow mass range selection of specific samples.

The LG spin and orbital angular momentum have no particular alignment,
and we see no significan alignments in our LG pairs, however for the alignment
between pair spins we found a slight alignment signature for $2\sigma$ sample as
can be seen in figure $5$.

@@

\section*{Acknowledgements}
REG was supported by Proyecto Financiamiento Basal PFB06 and Comite Mixto ESO.
